PEACE: {\underline P}arallel {\underline E}nvironment for {\underline A}ssembly and {\underline C}lustering of Gene {\underline E}xpression

### 2010-04-21 papers/NAR_web_server_2009/paper.sup.tex
Semi-final changes to the resubmission

\newcommand{\peace} {{\small PEACE}}
\newcommand{\wcd} {{\small WCD}}
\newcommand{\capthree} {{\small Cap3}}
\newcommand{\easycluster} {{\small EasyCluster}}

@@

\mc{In the \textsc{peace} implementation, we subdivide into three groups:
\begin{itemize}
\item Less than 150 ($w=50$, $T=40$, $t=20$, $u=4$).
\item Between 150 and 400 ($w=75$, $T=60$, $t=35$, $u=6$)
\item Greater than 400 ($w=100$, $T=80$, $t=50$, $t=50$).
\end{itemize}}

@@

\begin{figure}
  \centerline{\includegraphics[width=3.35in]{pics.d/SeJiT1T2x40.pdf}}
  \caption{Comparisons of Sensitivity, Jaccard Index, Type 1 error and
    Type 1 error, based on the
    average over 30 simulated Sanger Sequence ESTs sets derived from 100 zebra
    fish genes  (see
    Supplementary Materials, Section C, for more details).  Blue/Solid
    = \peace, Green/Dash = \wcd, Black/Dot-Dash = \capthree; vertical
    tics = 95\% confidence intervals on estimates.  Intervals are not
    presented for Type 1 error due to the effective lack of
    variance.}\label{SeJiT1T2130}
\end{figure}

@@

>>>>

\newcommand{\peace} {{\small PEACE}}
\newcommand{\wcd} {{\small WCD}}
\newcommand{\capthree} {{\small Cap3}}
\newcommand{\easycluster} {{\small EasyCluster}}
\newcommand{\metasim} {{\small MetaSim}}

@@

\mc{In the \textsc{peace} implementation, we subdivide into three groups:
\begin{itemize}
\item Less than 150 ($w=50$, $T=50$, $t=20$, $u=4$).
\item Between 150 and 400 ($w=75$, $T=75$, $t=35$, $u=6$)
\item Greater than 400 ($w=100$, $T=100$, $t=50$, $t=50$).
\end{itemize}}

@@

\begin{figure}
  \centerline{\includegraphics[width=3.35in]{pics.d/SeJiT1T2x130.pdf}}
  \caption{Comparisons of Sensitivity, Jaccard Index, Type 1 error and
    Type 1 error using the elevated threhold ($T=130$).  Based on the average
    over 30 simulated Sanger Sequence ESTs sets derived from 100 zebra
    fish genes (see Supplementary Materials, Section C, for more
    details).  Blue/Solid = \peace, Green/Dash = \wcd, Black/Dot-Dash
    = \capthree; vertical tics = 95\% confidence intervals on
    estimates.  Intervals are not presented for Type 1 error due to
    the effective lack of variance.}\label{SeJiT1T2130}
\end{figure}

@@

\section{Short Read Analysis}

\begin{table}[tbp]
\begin{center}
\begin{tiny}
\begin{tabular} {| c || c || c | c | c | c | c | c | c |}
\hline
 & 
& Sensitivity & Jaccard & \begin{tabular}{c} Type 1 \\
  error \end{tabular} & \begin{tabular}{c} Type 2 \\
  error \end{tabular} &
\begin{tabular}{c} Number \\ of  \\
    Clusters \end{tabular} & \begin{tabular}{c} Number \\ of \\
    Singletons \end{tabular}
    & \begin{tabular}{c} Single \\ processor \\ runtime (s) \end{tabular}\\
\hline
\hline   & \peace & 0.871 & 0.809 & 0.186 & 0.049 & 129 & 4 & 129 \\
\cline{2-9}  MetaSim 454 & \wcd(1) & 0.073 & 0.073 & 0.014 & 0.082 & 7028.500 & 5296.533 & 74 \\
\cline{2-9}  Simulation & \wcd(2) &  0.020 & 0.020 & 0.008 & 0.198 & 13085 & 10610 & 64 \\
\cline{2-9}  & \capthree & 0.005 & 0.005 & 0.005 & 0.565 & 19222 & 15425 & 132 \\
\hline
\hline Metasim  & \peace & 0.583 & 0.372 & 0.230 & 0.111 & 392.914 & 149.257 & 3454 \\
\cline{2-9} Illumina  & \capthree & 0.006 & 0.006 & 0.002 & 1.766 & 51663.057 & 30107.429 & 291 \\
\hline
\end{tabular}
\end{tiny}
\end{center}
\caption{Comparisons of runs on on short read data, as generated by
  \metasim \cite{Richter2008}; each figure is an average over 30 runs.
  For \wcd(1) we use wcd default parameters, while for \wcd(2) we set
  it to match the \peace\/ parameters ($w=75$, $T=60$); \wcd\/ was
  unable to return any results for Illumina data, hence has been
  omitted.  Each 454 simulation produced 25,000 reads from the 100
  zebra-fish transcripts, ranging  in size from 200bp to 270bp (aveage = 250bp,
  standard deviation = 17bp).  Each Illumina simulation produce 150K
  reads from the 100 zebra-fish transcript, each exactly 62bp.}\label{SRSim}
\end{table}
